Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-09-25 paper.tex
Add note about strut drag; resolves #43

Predictions for both the mean rotor power and drag coefficients at the optimal
tip speed ratio $\lambda_0 = 1.9$ are shown in
Figure~\ref{fig:br-cfd-perf-bar-chart}. In general, the 2-D CFD cases both
significantly overpredict turbine loading and therefore mechanical power output,
which is due to their increased blockage ratio, unresolved blade end effects,
and lack of blade support struts.

>>>>

Predictions for both the mean rotor power and drag coefficients at the optimal
tip speed ratio $\lambda_0 = 1.9$ are shown in
Figure~\ref{fig:br-cfd-perf-bar-chart}. In general, the 2-D CFD cases both
significantly overpredict turbine loading and therefore mechanical power output,
which is due to their increased blockage ratio, unresolved blade end effects,
and lack of blade support struts. Effects of blade support strut drag were
investigated experimentally by Rawlings~\cite{Rawlings2008}, showing that for a
rotor with six foil-shaped struts, parasitic losses would cause a 4 percentage
point reduction in $C_P$ at $\lambda=2$. Since the UNH-RVAT has only three
foil-shaped struts, it therefore follows that the overprediction by the 2-D
simulations is mostly attributable to blockage and end effects, rather than
support strut drag.
